Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
comment resuls in the middle of methods

Theses filters lead, taken individually, to worse performances  than filters
$f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
\begin{table}[ht]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Averaging} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
 with $f_1$, $f_2$ & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  \textbf{0.390} &  0.385 & \textbf{0.375}  \\
 with $f_1$, $f_2$, $f_3$, $f_4$ & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
\hline
\end{tabular}
\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
\end{table}

>>>>

\textcolor{red}{AJ: This paragraph and table should go in a separate section}
Theses filters lead, taken individually, to worse performances  than filters
$f_1$ and $f_2$ but averaging the results of all low-pass filters leads to better ROC AUC.
\begin{table}[ht]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Averaging} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
 with $f_1$, $f_2$ & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  \textbf{0.390} &  0.385 & \textbf{0.375}  \\
 with $f_1$, $f_2$, $f_3$, $f_4$ & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
\hline
\end{tabular}
\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
\end{table}
